# Introduction

## What is the Black Rock City Census?
The Census is a collaborative research project that started in 2002. Although 
the Black Rock City (BRC) Census project is technically a survey and not a 
literal census (where data is collected from every member of a population), 
our methodology allows us to report estimates that are representative of the 
entire population of BRC and not just on the individuals who 
participate actively in our data collection efforts.

While BRC Census has been producing reports since 2002, it is hard to compare 
recent data with reports from earlier years (before 2013) because of important 
differences in methodology, from a convenience sample of Census Lab 
visitors on-playa to a weighted online survey conducted post-event. 
The results in this report are estimates of the Black Rock City population. 
The true population values may differ from the presented estimates due to random 
variation in the sampling process. This report contains estimates from data 
collected in 2022 and, when possible, comparable estimates from 2013 through 
2018.

The BRC Census project is made possible through the extensive collective effort 
of volunteers, academic researchers, and Burning Man Project. Our thanks to 
everyone whose contributions went into the creation of this report!

## Methods
Since 2013, the BRC Census team has collected data in two phases: a random 
sample of participants entering the Burning Man event and a more comprehensive 
online survey after the event. During the Burning Man event in Black Rock City, 
Census volunteers conduct the random sample by administering a short 
socio-demographic survey to randomly selected Burners who agree to participate.
After the event, announcements about the online survey are sent out via email 
lists, social media, the Burning Man website and through other various
outreach programs. Results from the online survey are biased due to 
self-selection of Burners choosing to participate. To adjust for this bias
we choose weights for the online survey responses so that answers to key questions
asked on both surveys match.

All analyses were conducted using R version 4.2.2 [@R-base] and the anesrake [@R-anesrake] and survey [@R-survey] packages.  Graphics were created using the ggplot2 [@R-ggplot2] package, and this report was constructed using
R Bookdown [@R-bookdown].

This study was performed in accordance with the Declaration of Helsinki. This human study was approved by University of Nevada, Reno, Research Integrity - IRBNet ID:1903458-1. All parents, guardians, or next of kin provided verbal consent for the minors to participate in this study. Verbal consent was taken from all other participants at the time of interviews. The verbal consent process was documented by interviewers at the time of the interview. 

### Random Sample 
The random sample is designed with a goal of surveying 5\% to 10\% of the population 
of Black Rock City in a given year. The survey collection is stratified by 
location participants entered Black Rock City: the main gate, the airport, or 
on the Burner Express Bus (a shuttle service running from San Francisco and 
Reno into Black Rock City). Participants are chosen in a pseudo-random fashion 
by skipping a pre-selected number of cars driving in through gate or 
participants entering through the airport. Entire Burner Express Buses 
are randomly selected as a cluster sample.

The random sample collects data on 10 questions by giving selected participants
a short paper form to fill out:

* Day of arrival
* Age
* Number of prior Burning Man events attended
* English as a first language
* Gender
* US Resident or not
* Voting eligibility in the US
* US political party affiliation

### Online Survey 
The online survey is live Tuesday the week following and remains available 
for approximately a month. The survey comprises questions in the random
sample, demographic and socioeconomic questions, questions submitted by
the Burning Man Organization, and questions submitted by academic researchers.
Response rates for all surveys are given in the table below.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(kableExtra)
responseTable <- matrix(cbind(c("11,919", "11,676", "9,585", "7,137", 
                                "9,168", "8,745", "7,737", "8,382"),
                              c("68,000", "68,000", "70,000", "70,000", 
                                "70,000", "70,000", "80,000", "87,000"),
                              c("17%", "18%", "14%", "11%", "13%", "12%",
                              "10%", "10%")), ncol = 3)
rownames(responseTable) <- c(2013:2019, 2022)
responseTable |>
  kbl(col.names = c("Survey responses (n)", "BRC Population", "Response rate"),
      row.names = TRUE) |>
  kable_paper("striped", full_width = F) |>
  kable_styling() |>
  column_spec(column = 1:1, width_min = "9.5em")

```

### Weighting
Results from the online survey are weighted to adjust for selection bias. Weights
are chosen so that the distribution of responses for questions that appear in 
both the random sample and the online survey are nearly the same through a
process called post stratification or raking [@holt1979post; @debell2009computing]. 
For example, in 2022, the random
sample estimated 28.3\% of participants were virgins (attending their first burn),
but only 24.1\% of online sample particpants were virgins.  
Weighting responses of the online brings this estimate up to 28.3\% to match the random sample.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(scales)
plotDat <- data.frame(est = c(0.283, 0.241, 0.283),
                      label = c("28.3%", "24.1%", "28.3%"),
                      type = factor(c("Random sample", 
                                      "Online survey (unweighted)",
                                      "Online survey (weighted)"),
                                    levels = c("Random sample", 
                                      "Online survey (unweighted)",
                                      "Online survey (weighted)")))
ggplot(plotDat, aes(x = type, y = est)) +
  geom_bar(stat = "identity", fill = "#EA008B") +
  geom_text(aes(label = label), vjust = -1.5, colour = "black") +
  scale_y_continuous(labels = percent, limits = c(0, 0.4)) +
  theme_bw() +
  labs(x = "", y = "Participants in 2022 (%)",
       title = "Percent virgin burners in 2022")
```


